---
title: "ASSIGNMENT-1"
author: "sarthak verma"
date: "23 August 2017"
output: html_document
---
```{r}
library(dplyr)
library(knitr)
parli=read.csv("C://Users//Administrator//Desktop//parliament.csv")
dim(parli)
View(parli)


```
#1.Identify year wise total number of electors and voters.Also compute percentage of voters.
```{r}
year_wise=parli %>% group_by(YEAR,PC) %>% summarise(total_votes=sum(VOTES,na.rm=TRUE))
year_wise
year_wise = parli %>% group_by(YEAR) %>% summarise(total_ELECTORS=sum(unique(ELECTORS))) 
year_wise
year_wise = parli %>% group_by(YEAR) %>% summarise(pct_voters=sum(VOTES)*100/sum(unique(ELECTORS)))
year_wise
```





##2.Identify year wise percentage of male and female candidates.
##PERCENTAGE MALES WAS HIGHEST IN 1996
```{r}
parli_male=filter(parli,SEX=='M')
View(parli_male)
parli_female=filter(parli,SEX=='F')
View(parli_female)
parli_male_count= parli_male %>% group_by(YEAR) %>% summarise(males=n()) %>% arrange(-YEAR)
parli_female_count= parli_female %>% group_by(YEAR) %>% summarise(females=n()) %>% arrange(-YEAR)
election_count=merge(parli_male_count,parli_female_count,by.x='YEAR',by.y='YEAR')
election_count=election_count %>% arrange(-males,-females)
election_count
total=election_count$males+election_count$females
total
percentage_males=round((election_count$males/total)*100,2)
percentage_males
percentage_females=round((election_count$females/total)*100,2)
percentage_females
election_count=cbind(election_count,percentage_males)
election_count=cbind(election_count,percentage_females)
election_count
```

##3.compute party wise total number of candidates won so far?Display top ten parties alone
##INC WAS THE TOP PARTY WITH 3348 CANDIDATES
```{r}
candidate_won = filter(parli,Position == 1)
party_wise = candidate_won %>% group_by(PARTY) %>% summarise(winning_candidate=n()) %>% arrange(-winning_candidate)
head(party_wise,10)

```

##4.Identify year wise which party has won (based upon total number constituencies won)
##INC WON MAXIMUM SEATS 
```{r}
party_won = filter(parli,Position == 1)
a=party_won %>% group_by(PARTY,YEAR) %>% summarise(winnum=n())
a=a %>% group_by(YEAR) %>% filter(winnum==max(winnum)) %>% arrange(-YEAR)
a

```

##5.Identify year wise percentage of winning for female candidates
##HIGHEST PERCENTAGE WAS IN 2009
```{r}
parli_male=filter(parli,SEX=='M',Position==1)
View(parli_male)
parli_female=filter(parli,SEX=='F',Position==1)
View(parli_female)
parli_male_count= parli_male %>% group_by(YEAR) %>% summarise(males=n()) %>% arrange(-YEAR)
parli_female_count= parli_female %>% group_by(YEAR) %>% summarise(females=n()) %>% arrange(-YEAR)
election_count=merge(parli_male_count,parli_female_count,by.x='YEAR',by.y='YEAR')
election_count=election_count %>% arrange(-males,-females)
election_count
total=election_count$males+election_count$females
total
percentage_females=round((election_count$females/total)*100,2)
percentage_females
election_count=cbind(election_count,percentage_females) %>% arrange(-YEAR)
election_count

```














```





















