---
title: "readmission"
author: "SARTHAK VERMA"
date: "30 December 2017"
output: html_document
---
```{r}
library(dplyr)
library(ggplot2)
library(knitr)
read=read.csv('C://Users//Administrator//Desktop//READMISSION REDUCTION.csv')
summary(read)
View(read)
str(read)
dim(read)
typeof(read)
read$Footnote=NULL
View(read)
dim(read)
colSums(is.na(read))
#converting data types
read$Hospital.Name=as.character(read$Hospital.Name)
read$State=as.character(read$State)
read$Number.of.Discharges=as.numeric(read$Number.of.Discharges)
read$Expected.Readmission.Rate=as.numeric(read$Expected.Readmission.Rate)
read$Expected.Readmission.Rate=as.numeric(read$Expected.Readmission.Rate)
read$Number.of.Readmissions=as.numeric(read$Number.of.Readmissions)
read$Expected.Readmission.Rate=as.numeric(read$Expected.Readmission.Rate)
read$Excess.Readmission.Ratio=as.numeric(read$Excess.Readmission.Ratio)
read$Predicted.Readmission.Rate=as.numeric(read$Predicted.Readmission.Rate)
read$Excess.Readmission.Ratio=as.numeric(read$Excess.Readmission.Ratio)
str(read)
```
#calculating total number of discharges according to hospital name
```{r}
library(zoo)
na.locf(read$Number.of.Discharges)
total_discharges = read %>% group_by(Hospital.Name) %>% summarise(total_discharges=n()) %>% arrange(-total_discharges)
top_10=head(total_discharges,10)
top_10
P1=ggplot(top_10,aes(x=Hospital.Name,y=total_discharges)) + geom_bar(stat='identity',width = 0.6,aes(fill=total_discharges))
P1

#reordering the bars
P2=ggplot(top_10,aes(x=reorder(Hospital.Name,-total_discharges),y=total_discharges)) + geom_bar(stat='identity',width = .6,aes(fill=total_discharges))
P2
P3=P2 +theme(axis.text.x = element_text(angle = 90))
P3
```
#Removing the background grid

```{r}
#arranging x axis
P4=P3 + theme(axis.text.x = element_text(angle = 90))
P4


#removing x axis text and ticks
P5 = P4 + theme(axis.text.x=element_blank(),axis.title.x=element_blank() , axis.ticks.x= element_blank())
P5
```
## Adjusting the legends
# Hiding the legend title
```{r}
P6=P5 +theme(legend.title = element_blank())
P6
#changing the position of legend
P7=P6+theme(legend.position = 'bottom')
P7

```

# Changing the legends size (text Plus blocks)
```{r}
P8=P7 + theme(legend.key.width=unit(.2,'cm'))
P8
```



```{r}
# Renaming x-axis and Y-axis and plot name

P9 = P8 + labs(subtitle="Top 10 discharges", 
               y="Number of discharges", x="hospital Name", title="Bar Plot", 
               caption = "Source: MCI")
P9

```
#CREATING HISTOGRAM AND SCATTERPLOT
```{r}
hist(read$Number.of.Discharges)
boxplot(read$Number.of.Discharges)
scatter.smooth(read$Number.of.Discharges)# scatter plot
```

#most frequently appearing state

```{r}
unique(read$State)
by_state=sort(table(read$State),decreasing = TRUE)
a=head(by_state)
a
b=as.data.frame(a)
b
c=head(b)
d=ggplot(c,aes(x=reorder(Var1,-Freq),y=Freq)) + geom_bar(stat = 'identity',width=.6,aes(fill=Var1))
d
p1=d+theme(axis.title.x = element_blank(),axis.ticks.x = element_blank(),axis.title.y = element_blank())
p1


```
 ##calculating statewise average expected readmission rate
 
```{r}
class(read$Expected.Readmission.Rate)
read$Expected.Readmission.Ratio=as.numeric(read$Expected.Readmission.Rate)
class(read$Expected.Readmission.Rate)
read11=read %>% group_by(State) %>% summarise(sum_rer=mean(Expected.Readmission.Rate)) %>% arrange(-sum_rer)
a=head(read11,10)
#REORDERING THE BAR GRAPHS
p1=ggplot(a,aes(x=reorder(State,-sum_rer),y=sum_rer,group==1)) + geom_bar(stat ='identity',width = .6,aes(fill=State))
p2=p1+theme_bw()
p2
p3=p2 + theme(axis.text.x = element_text(angle=90))
p3
p4=p3+theme(axis.ticks.x = element_blank())
p4
p5=p4+theme(axis.text.x = element_blank(),axis.title.x = element_blank())
p5
p6=p5+theme(legend.title = element_blank(),legend.position = "bottom")
p6
p7=p6+theme(axis.title.y=element_blank(),axis.ticks.y = element_blank(),axis.text = element_blank())
p7



```

```{r}
str(read)
```
##calculating hospital wise total excess readmission ratio
```{r}
a=read %>% group_by(Hospital.Name) %>% summarise(t_e_r=sum(Excess.Readmission.Ratio)) %>% arrange(-t_e_r)
b=head(a)
b
p1=ggplot(b,aes(x=Hospital.Name,y=t_e_r))+geom_bar(stat = 'identity',width = 0.5,aes(fill=t_e_r))
p20=p1+theme(axis.text.x = element_text(angle=90),axis.text.y=element_blank(),axis.ticks.x = element_blank(),axis.ticks.y = element_blank(),axis.title.y = element_blank(),axis.title.x = element_blank())
p20
```

#frequency distribution of state column
```{r}
freq_dist=read %>% group_by(State) %>%  summarise(count=n()) %>% arrange(-count)
freq_dist
a=head(freq_dist)
b=ggplot(a,aes(x=reorder(State,-count),y=count,fill=State)) + geom_bar(stat = 'identity',width=.5)
b
p1=b+theme(axis.title.x = element_blank(),axis.ticks.x = element_blank(),axis.text.x = element_blank(),axis.title.y = element_blank(),axis.ticks.y = element_blank())
p1
```

##hospital wise frequency distribution
```{r}
freq_dist_h=read %>% group_by(Hospital.Name) %>% summarise(count=n()) %>% arrange(-count)
a=head(freq_dist_h)
library(ggplot2)
b=ggplot(a,aes(x=reorder(Hospital.Name,-count),y=count,fill=Hospital.Name)) + geom_bar(stat = 'identity',width = .6)
b
p1=b+theme(axis.text.x = element_text(angle = 90),axis.title.x = element_blank(),axis.title.y = element_blank(),axis.ticks.x = element_blank())
p1
```

#scatter plot between predicted readmission rate and expected readmission rate for state AL

```{r}
state_wise=filter(read,State=='AL')
a=head(state_wise)
ggplot(a,aes(x=Predicted.Readmission.Rate,y=Expected.Readmission.Rate)) + geom_point() + geom_smooth()
```







