---
title: "Problem Statement"
author: "Sarthak Verma"
date: "22 September 2017"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(dplyr)
library(ggplot2)
library(knitr)
library(corrplot)

```


#Importing the dataset
- Describing the dataset
 - finding no. of columns, rows and class types of columns
```{r}
congress = read.csv("D:/Problem1/Data Set.csv", na.strings = '')

dim(congress)

names(congress)

str(congress)
```

# Data sanity

- Calculating percentage of NAs in each column
```{r}
colSums(is.na(congress)/nrow(congress)*100)

```


#Data Cleaning
- converting specific column types to their respective class
- deriving a new Full name column combining first name, middlename and last name
- creating date column
```{r}
congress$firstname = as.character(congress$firstname)
congress$middlename = as.character(congress$middlename)
congress$lastname = as.character(congress$lastname)
congress$suffix = gsub(congress$suffix,pattern = 'NA',replacement = '')
congress$suffix = as.character(congress$suffix)

congress$X = NULL
congress$X.1 = NULL

# Deriving a new Name column

congress$name = paste(congress$firstname,congress$middlename,congress$lastname, sep = ' ')

congress$birthday = as.Date(congress$birthday,'%Y-%m-%d')
congress$termstart = as.character(congress$termstart)
congress$termstart = as.Date(congress$termstart, '%m/%d/%Y')

congress$age = as.character(congress$age)
congress$age = as.numeric(congress$age)

congress$state = as.character(congress$state)

View(congress[which(nchar(congress$state)>2),])
#congress[which(nchar(congress$state)>2),]$birthday = congress[which(nchar(congress$state)>2),]$state

congress$party = as.character(congress$party)
congress$incumbent = as.character(congress$incumbent)


```

#Data Imputation
- Imputing the missing ages with mean age 
```{r}
congress1 = congress
congress1[which(is.na(congress1$age)),]$age = 53.31

congress1[congress1$party == '3/15/1926',]
congress1 = congress1[-c(10018,10549,11074,11605,12140,12663)]
```

# Analysis
- Numeric 
- creating age groups (derived column)

##Univariate analysis of Age
```{r}
congress1$age_grp = cut(congress1$age, breaks = c(0,30,40,60,80,Inf),labels = c("0-30","30-40","40-60","60-80","80+"))

age_freq = congress1 %>% group_by(age_grp) %>% summarise(Count = n())
kable(age_freq[1:5,])

ggplot(data= age_freq) + geom_bar(aes(x = age_grp, y= Count,fill = age_grp),stat = 'identity')

hist(congress1$age)

mean(congress1$age)
```


```{r}
boxplot(congress1$age)

quantile(congress1$age)

iqr = 60.5-45.5  #Q3-Q1
iqr

upper_whisker = 60.5 + 1.5*iqr
upper_whisker

outlier_perc = sum(congress1$age>83, na.rm = TRUE)*100/nrow(congress1) 
outlier_perc

```



# Calculate avg age of people for same first name in each chamber

```{r}
house = congress1 %>% filter(chamber == 'house')
senate = congress1 %>% filter(chamber == 'senate')
avg_age_house = house %>% group_by(firstname) %>% summarise(Avg_age = mean(age, na.rm=TRUE)) %>% arrange(-Avg_age)
avg_age_house

avg_age_senate = senate %>% group_by(firstname) %>% summarise(Avg_age = mean(age, na.rm=TRUE)) %>% arrange(-Avg_age)
avg_age_senate


```
#Bi variate 

```{r}
incumbent_freq = congress1 %>% group_by(incumbent) %>% summarise(Total_count = n()) %>% arrange(-Total_count)
kable(incumbent_freq[1:5,])

inc_party = senate %>% group_by(party,incumbent) %>% summarise(count = n()) %>% arrange(-count)
kable(inc_party[1:6,])


```

# which party has won how many times in both chambers
```{r}
senate_won = senate %>% group_by(congress,party) %>% summarise(count = n()) 
kable(senate_won[1:10,])

house_won = house %>% group_by(congress,party) %>% summarise(count = n()) %>% arrange(-congress) 
kable(house_won[1:11,])

ggplot(senate_won, aes(x= congress, y = count)) + geom_bar(aes(fill = party),stat = 'identity')

ggplot(house_won, aes(x= congress, y = count)) + geom_bar(aes(fill = party),stat = 'identity',show.legend = F) + xlab('D = blue, R-pink') 
```

# When same party was in majority in both houses
```{r}
win = congress1 %>% group_by(congress,chamber,party) %>% summarise(count =n())  


win_party = win %>%group_by(congress,chamber) %>% filter(count == max(count))


win_congress = subset(win_party,select =c(congress,chamber,party))
win_congress_plot = win_congress %>% mutate(govt = ifelse(party == 'R',1,ifelse(party=='D',-1,0)),party = party) 
plot = win_congress_plot %>% group_by(congress,party) %>% summarise(Same_or_diff = sum(govt,na.rm =T))
ggplot(data = plot) + geom_bar(aes(x=congress, y = Same_or_diff, fill = party),stat = 'identity')

```

# pca
```{r}
newdata = congress[,c(1,13)]
newdata$age = as.character(newdata$age)
newdata$age = as.numeric(newdata$age)

newdata[which(is.na(newdata$age)),]$age = 53.31


## Scaling the data
scaled_data=scale(newdata)


##getting eigen values 
eval=eigen(cor(scaled_data))$values
eval
evec=eigen(cor(scaled_data))$vectors
evec

pcs_data=scaled_data %*% evec
dim(pcs_data)


corrplot(cor(pcs_data))
cumsum(eval /length(eval)*100)

vars_cum=cumsum(eval / length(eval) * 100)
a = matrix(c(0,2,95,95), 2,2, byrow= FALSE)
{plot(a, type='l', col='blue')
lines(vars_cum, col='red')}

data_rc = pcs_data %*% t(evec)
data_rc= as.data.frame(data_rc)

names(data_rc) = names(newdata)


scaled_data=as.data.frame(scaled_data)
plot(scaled_data$age, type='l', col='orange')
lines(data_rc$age, col='blue')

```

