---
title: "IMDB ANALYSIS"
author: "sarthak verma"
date: "14 September 2017"
output: html_document
---
```{r}
library(dplyr)
library(knitr)
imdb=read.csv("C://Users//Administrator//Desktop//imdb.csv")
dim(imdb)
View(imdb)
library(ggplot2)
help("imdb")
data(imdb)
```
#calculating number of nulls in each column
```{r}
x=c()
for(i in 1: ncol(imdb))
{
  nulls_count = length(which(is.na(imdb)))
  x=append(x,nulls_count)
  print(nulls_count)
}
```

#checking data sanity-calculating missing values in dataset
```{r}
colSums(is.na(imdb))

```
#checking frequency distribution for each column
```{r}
col_name="director_name"
data=imdb %>% group_by(category = get(col_name)) %>% summarise(count=n())
data

```
#calculating percentage of director name column
```{r}
col_name="director_name"
data=imdb %>% group_by(category = get(col_name)) %>% summarise(count=n() * 100/nrow(imdb))
data
```
#frequency distribution for num_critic_for_reviews
```{r}
col_name="duration"
imdb1=imdb %>% group_by(category=get(col_name)) %>% summarise(count=n() *100/nrow(imdb)) %>% arrange(-count)
imdb1




```
#creating histograms of different column
```{r}
hist(imdb$actor_1_facebook_likes)
hist(imdb$director_facebook_likes)
```
#creating boxplot
```{r}
boxplot(imdb$actor_3_facebook_likes)
```
#CALCULATING OUTLIERS FOR DURATION 
```{r}
quantile(imdb$duration,na.rm = TRUE)
IQR(imdb$duration,na.rm = TRUE)
```

#outlier is 155.5
```{r}
sum(imdb$duration>155.5,na.rm = TRUE)*100/nrow(imdb)
```
```{r}
data11=imdb %>% group_by(genres) %>% summarise(count=n()) %>% arrange(-count)
data11
```
#univariate plots section

```{r}
imdb1 <- imdb %>% 
  group_by(director_name) %>%
  summarise(count = n())%>%
  filter(count >10, count <50) %>% arrange(-count)
imdb1
ggplot(imdb1,aes(x=director_name,y=count)) + geom_bar(stat='identity')
  

```






